\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-10-23 AffineLieAlgebras/InformalNotes/article.tex
More work

@@

\begin{equation}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation}
\end{equation}
where the set 
\begin{equation}
\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
\label{fan-defined}
\end{equation}

\section{Algorithm}
\label{sec:algorithm}

@@

B2->A1 etc.

@@

Branching of affine to affine and affine to classical.
\subsection{Physical applications}
\label{sec:phys-appl}

>>>>

\begin{comment}
  Fix this discussion of natural ordering
\end{comment}

@@

\begin{equation}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation}
\end{equation}
where the set 
\begin{equation}
\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
\label{fan-defined}
\end{equation}
\begin{comment}
  Say something about the end of the proof
\end{comment}

\section{Algorithm}
\label{sec:algorithm}
\begin{enumerate}
\item Construct the set of anomalous points of the algebra $\mathfrak{g}$
\item Calculate the dimensions of the corresponding modules $L_{\mathfrak{a}_{\bot}}$.
\item Calculate anomalous branching coefficients in the main Weyl chamber of the subalgebra $\mathfrak{a}$
\item \dots
\item PROFIT !!!
\end{enumerate}

@@

\subsubsection{Regular embedding of $A_1$ into $B_2$}
\label{sec:regul-embedd-a_1}

\subsubsection{Something high-dimensional}
\label{sec:someth-high-dimens}

@@

\subsection{Embedding of finite-dimensional algebra into affine algebra}
\label{sec:embedd-finite-dimens}

\subsection{Embedding of the affine algebra into affine algebra}
\label{sec:embedd-affine-algebr}

\subsection{Physical applications}
\label{sec:phys-appl}
